Age-related changes in plant growth and traits

### 2016-04-28 Accessory_figs_20160218.Rmd
small changes

plot(prepollen_failure_per_seed~seed_size,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species))
mod <- lm(log(propagule_inv)~log(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
summary(mod)

@@

@@

write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table03_AccCosts_by_Species.csv",row.names=FALSE)
```

@@

acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```

>>>>

plot(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),pch=16,log="",col=col.spp(species))
mod <- lm(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"))
summary(mod)

@@

#seed size by propagule investment - all species
mod <- sma(propagule_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
summary(mod)
plot(propagule_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

#seed size by propagule investment - without EPMI
mod <- sma(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
summary(mod)
plot(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))

#seed size by reproductive investment - all species
mod <- sma(repro_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
summary(mod)
plot(repro_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

#seed size by reproductive investment - without EPMI
mod <- sma(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
summary(mod)
plot(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))

#seed size by reproductive investment - all species
mod <- sma(total_weight_0 ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
summary(mod)
plot(total_weight_0 ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))

@@

write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
```

@@

slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal","total postpollen")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
```
plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")
